---
title: "Final Project"
author: "Conrad Polkosnik"
date: "4/20/2018"
output: word_document
---

# Loading Packages
```{r}
library(quantmod)   # for stock prices & stock analysis
library(xts)        # extensible time series 
library(tidyverse)  # ggplot2,dplyr, tidyr, readr, tibble
library(stringr)    # working with strings
library (magrittr)  # for pipe operator
```


# Downloading Stock Data
```{r}
# Calling quantmod
library("quantmod")

# Gathering historical stock data for Exxon Mobil since January 2nd, 1970
getSymbols("XOM", src='yahoo', from="1970-01-02")

```

# Understanding scraped data pulled
```{r}
# Calling magrittr
library(magrittr) #for pipe operator

XOM %>% class()

XOM %>% str()

XOM %>% head()
```

# Visualize trend of stock price over time
```{r}
XOM %>% Ad() %>% chartSeries()
```


# Technical Analysis for more recent movement in 2018
```{r}
XOM %>% chartSeries(TA='addBBands();
                    addBBands(draw="p");
                    addVo();
                    addMACD()',
                    subset='2018',
                    theme="white"
                    )
```


# Gathering log daily returns for XOM
```{r}
XOM %>% Ad() %>% dailyReturn(type = 'log') %>% head()
```

# Using log returns to analyze distribution
```{r}
XOMLogReturns <- XOM %>% Ad() %>% dailyReturn(type = "log")

names(XOMLogReturns) <- "XOM.Log.Returns"

# Plotting the log returns using a histogram to analyze distribution
library(ggplot2)
XOMLogReturns %>% ggplot(aes(x = XOM.Log.Returns)) + geom_histogram(bins = 100) + geom_density() + geom_rug(alpha = 0.5)
```

# Setting probabilities for study of liklihood
```{r}
Probabilities <- c(.005, .025, .25, .5, .75, .975, .995)

DistributionalLogReturns <- XOMLogReturns %>% quantile(probs = Probabilities, na.rm = TRUE)

DistributionalLogReturns
```

# Finding Mean and Standard Dev. Log returns
```{r}
MeanLogReturns <- mean(XOMLogReturns, na.rm = TRUE)
StDevLogReturns <- sd(XOMLogReturns, na.rm = TRUE)

MeanLogReturns
StDevLogReturns
```

# Finding daily average increase or decrease in return
```{r}
MeanLogReturns %>% exp()
```


# Random Walk
```{r}
# Setting Parameters
N <- 252 # number of trading days
mu <- MeanLogReturns
sigma <- StDevLogReturns
day <- 1:N

# Setting variable of interest
InitialPrices <- XOM$XOM.Adjusted[[nrow(XOM$XOM.Adjusted)]]

# Setting RNG and simulating
set.seed(386) # for reproducibility
Price  <- c(InitialPrices, rep(NA, N-1))
for(i in 2:N) {
    Price[i] <- Price[i-1] * exp(rnorm(1, mu, sigma)) # using rnorm since we have normal distribution
              }

# Calling tidyverse
library(tidyverse)
PriceSimulation <- cbind(day, Price) %>% as_tibble()

# Visualize price simulation
PriceSimulation %>%
    ggplot(aes(day, Price)) +
    geom_line() +
    ggtitle(str_c("XOM: Simulated Prices for ", N," Trading Days"))
```

# Monte Carlo Simulation for Random Walk
```{r}
# Setting Parameters
N     <- 252 # Number of Stock Price Simulations
M     <- 100  # Number of Monte Carlo Simulations   
mu    <- MeanLogReturns
sigma <- StDevLogReturns
day <- 1:N

# Setting variable of interest
InitialPrices <- XOM$XOM.Adjusted[[nrow(XOM$XOM.Adjusted)]]

# Simulate prices using for loop and Monte Carlo Matrix
set.seed(386)
MonteCarloMatrix <- matrix(nrow = N, ncol = M)
for (j in 1:M) {
    MonteCarloMatrix[[1, j]] <- InitialPrices
    for(i in 2:N) {
        MonteCarloMatrix[[i, j]] <- MonteCarloMatrix[[i - 1, j]] * exp(rnorm(1, mu, sigma))
                  }
               }

# Organizing data frame and format
PriceSimulation <- cbind(day, MonteCarloMatrix) %>% as_tibble() 
nm <- str_c("Sim.", seq(1, M))
nm <- c("Day", nm)

names(PriceSimulation) <- nm
PriceSimulation <- PriceSimulation %>%
    gather(key = "Simulation", value = "Stock_Price", -(Day))

# Visualization
PriceSimulation %>%
    ggplot(aes(x = Day, y = Stock_Price, Group = Simulation)) + 
    geom_line(alpha = 0.1) +
    ggtitle(str_c("XOM: ", M, 
                  " Monte Carlo Simulations for Prices Over ", N, 
                  " Trading Days"))
```

# Stock price estimation and likelihood
```{r}
EstimatedStockPrices <- PriceSimulation %>% filter(Day == max(Day)) # estimating stock price at end of 252 simulated trading days

Probabilities <- c(.005, .025, .25, .5, .75, .975, .995)

DistributionalEstimatedStockPrices <- quantile(EstimatedStockPrices$Stock_Price, probs = Probabilities) # estimating stock prices based on probabilities of likelihood

DistributionalEstimatedStockPrices %>% round(2) # rounding off to two decimal places
```





